---
title: "ea4"
author: "Patrick Bichiou"
date: "2024-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(readr)
```

# import the data("iris")
```{r}
Iris <- data(iris)
```

# make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point(size = 3) +  # Adjust point size for better visibility
  labs(title = "Sepal Length vs. Sepal Width by Species",
       x = "Sepal Length (cm)", y = "Sepal Width (cm)") +
  theme_bw()  # Use black and white theme for better readability
```

# add regression line for the previous plot with the whole dataset (regardless of the species)
```{r}
ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) +
  geom_point(size = 3, color = "grey") +
  geom_smooth(method = lm) +  # Add linear regression line
  labs(title = "Sepal Length vs. Sepal Width with Regression Line",
       x = "Sepal Length (cm)", y = "Sepal Width (cm)") +
  theme_bw()
```

# calculate the Pearson correlation for this plot
```{r}
cor(iris$Sepal.Length, iris$Sepal.Width, method = 'pearson')
```

# make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors
```{r}
ggplot(iris, aes(x = Species, y = Petal.Width, color = Species)) +
  geom_boxplot() +
  labs(title = "Distribution of Petal Width by Species",
       x = "Species", y = "Petal Width (cm)") +
  theme_bw()
```

# make the histogram for Petal.Width with 3 species separately in x-axis in different colors
```{r}
ggplot(iris, aes(x = Petal.Width)) +
  geom_histogram(binwidth=0.2, color="black", aes(fill=Species)) +
  labs(title = "Distribution of Petal Width by Species (Histogram)", x = "Species", y = "Frequency")
```

# run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species
```{r}
x <- iris[iris$Species == "setosa", ]$Petal.Width
y <- iris[iris$Species == "versicolor", ]$Petal.Width
t.test(x, y)
```

# Interpretation of t-test results:
#  - A low p-value (< 0.05) indicates statistically significant difference in Petal.Width between setosa and versicolor.
#  - A high p-value (> 0.05) suggests no significant difference.
#  For our example the p-value is 2.2e-16 (0,00000000000000022) < 0.05 , so it is significant